Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-12 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Madrzy_Thesis: update figure names and tex file

Examples of a set of TIFF images for each fuel are shown in Figures .~\ref{flame_height_comp_FHNG80_1} through .~\ref{flame_height_comp_FHPUF_1}.   Each figure has 56 sequential images from the video segment.  The images total almost 2~s of actual burn time.  Notice how the flame height cycles up and down in each of the sequences.  These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss and extreme (minimum or maximum) position when compared to the still photographs.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/flame height comp FHNG80-1.png}\\
	\caption[Example of sequential video frames sampled from a natural gas fueled experiment]{Example of sequential video frames sampled from a natural gas fueled experiment.  In this set of images, which spans almost two seconds, the visual continuous flame height fluctuates from approximately 0.6 m to 1.1 m.}
	\label{flame_height_comp_FHNG80_1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/flame height comp FHGAS-1.png}\\
	\caption[Example of sequential video frames sampled from a gasoline fueled experiment]{Example of sequential video frames sampled from a gasoline fueled experiment.  In this set of images which spans almost two seconds the visual continuous flame height fluctuates from approximately 0.6 m to 1.1 m.}
	\label{flame_height_comp_FHGAS_1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/flame height comp FHPUF-1.png}\\
	\caption[Example of sequential video frames sampled from a polyurethane foam fueled experiment]{Example of sequential video frames sampled from a polyurethane foam fueled experiment.  In this set of images which spans almost two seconds the continuous visual flame height fluctuates from 0.4 m to 0.9 m.}
	\label{flame_height_comp_FHPUF_1}
\end{figure}

>>>>

Examples of a set of TIFF images for each fuel are shown in Figures~\ref{flame_height_comp_FHNG80_1} through \ref{flame_height_comp_FHPUF_1}.   Each figure has 56 sequential images from the video segment.  The images total almost 2~s of actual burn time.  Notice how the flame height cycles up and down in each of the sequences.  These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss and extreme (minimum or maximum) position when compared to the still photographs.
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/flame_height_comp_FHNG80}\\
	\caption[Example of sequential video frames sampled from a natural gas fueled experiment]{Example of sequential video frames sampled from a natural gas fueled experiment.  In this set of images, which spans almost two seconds, the visual continuous flame height fluctuates from approximately 0.6 m to 1.1 m.}
	\label{flame_height_comp_FHNG80_1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/flame_height_comp_FHGAS}\\
	\caption[Example of sequential video frames sampled from a gasoline fueled experiment]{Example of sequential video frames sampled from a gasoline fueled experiment.  In this set of images which spans almost two seconds the visual continuous flame height fluctuates from approximately 0.6 m to 1.1 m.}
	\label{flame_height_comp_FHGAS_1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/flame_height_comp_FHPUF}\\
	\caption[Example of sequential video frames sampled from a polyurethane foam fueled experiment]{Example of sequential video frames sampled from a polyurethane foam fueled experiment.  In this set of images which spans almost two seconds the continuous visual flame height fluctuates from 0.4 m to 0.9 m.}
	\label{flame_height_comp_FHPUF_1}
\end{figure}
